Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-08-25 paper/uist_2016/paper.tex
restoring unintended changes..

Preserving memorable moments is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% fare of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

>>>>

Capturing a memory is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.
